A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-09-13 tex/sec6-formalisation.tex
[ tex ] Fix the mishap in References

Our formal induction proofs typically consist of mutual definitions for the inductive type of derivations, for a list of arguments, for an extension context, and sometimes for an operation separately.

>>>>

Our formal proofs of induction typically consist of mutual proofs for the inductive type of derivations, for a list of arguments, for an extension context, and sometimes for the case of operations for clarity.
